Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-17 SDSS-2023/testing-charts-accuracy.qmd
a bit more structure thinking in the results section

Description of respondents -- \# of respondents in each round, broad overview of demo characteristics(?), raw sample size and effective sample size

>>>>

Description of respondents

-   \# of respondents in each round

-   broad overview of demo characteristics(?)

-   raw sample size and effective sample size

Paragraph on combining samples across rounds

-   Pull from analysis doc

-   When combining responses from multiple rounds, we make weighting adjustments to ensure that each weights in each sample are properly calibrated to the population total across both rounds.
    **NEED ED REVIEW OF THIS LANGUAGE.** This adjustment is completed as follows: \[insert Heike text from analysis doc here\].

Test 1

-   Alignment in stacked bars

    -   Accuracy and responses

    -

Test 2

-   Structure of stacked bars

Test 3

-   Facetted bars and pies
